A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-10 src/paper.tex
WIP: Front controller pattern

The application hosting infrastructure (AHI) consists of a server environment that provides the necessary computing resources to run a web application and make it available to client applications. This infrastructure can be owned by the CP or it can be hired from a third party service provider. As a matter of fact, the web applications hosted in the AHI are responsible for providing the interactive content that can be accessed by the second screen clients. In addition, the web applications offer features for storing and processing data.

Cloud computing can be used to quickly scale up and scale down according to workload demands. Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting to consider the use of a cloud based platform for storing and processing data~\cite{Lee2010}.

>>>>

The application hosting infrastructure (AHI) consists of a server environment that provides the necessary computing resources to run a web application and make it available to client applications. This infrastructure can be owned by the CP or it can be hired from a third party service provider. As a matter of fact, the web applications hosted in the AHI are responsible for providing the interactive content that can be accessed by the second screen clients. In addition, the web applications offer features to store and to process interaction data obtained from the viewers.

The TV domain has the potential of facing very different audience ratings and the amount of viewers using a particular iTV service can drastically change during the day. So, an important requirement for shared iTV services is to dynamically scale up and down the service according to workload demands. Researchers have proposed novel ideas based on cloud-computing environments to tackle this requirement~\cite{Lee2010,Lai2011}. Since the architecture presented this paper is intended for a potentially large amount of viewers, the use of a cloud-computing infrastructure is considered to handle the requests from client applications.
